### 2020-06-05 tbf.tex

\begin{figure}[bt]
  \begin{center}
    \includegraphics[trim={0 1em 0 1em},clip,width=\columnwidth]{figs/MTBF_GPUwise.pdf}
  \end{center}
  \caption{Distribution of device-level MTBFs due to DBE and OTB failures across all GPUs during the
entire lifetime of the machine. DBE and OTB events are separated for each GPU to distinguish between 
the failure pattern of each event type. Data includes both old and new batch of GPUs with the new ones 
mostly having MTBFs around or less than 3 years.}
  \label{fig:Device_MTBFs}
\end{figure}
A histogram of MTBFs measured across GPUs which had at least one failure event is shown 
in \rev{Fig.}~\ref{fig:Device_MTBFs}. This is a practical assessment of device reliabilities 
as opposed to those provided in the device datasheet. The failures are tracked using the
\rev{{\em SN}} of the GPUs even though a GPU might have been placed at different locations in the 
machine during its lifetime. The time to the first failure on a device is measured by taking
the insert time as the reference point, whereas, a simple difference is taken for subsequent
failures. It can be noticed that MTBFs due to DBE and OTB failures of most GPUs are clustered around 
25,000 hours or 2.8 years. This corresponds to the lifetime of most GPUs in the system after accounting 
for relocations and replacements done in the machine. Almost all of the new batch of GPUs lie below 
the average since most have a lifetime close to 3 years. We point out
that the new batch had a much smaller number of failures than
the old batch as we highlight in the next section.

@@

%\begin{figure}[bt]
%  \begin{center}
%    \includegraphics[width=\columnwidth]{figs/MTBF_CageWise.pdf}
%  \end{center}
%  \caption{MTBFs due to either DBEs or OTBs across the GPUs located in different cages.}
%  \label{fig:CageWise_MTBFs}
%\end{figure}

%\fix{Figure~\ref{fig:CageWise_MTBFs} shows temperature effect clearly. Should we move this 
%result to later in the paper?}

@@

When GPU replacements start to take place in late 
2016, it triggers a slight increase in MTBF. However, this change only lasts until 2018-Q1, when we see another 
downward trend of system MTBF. Incidentally, 2018-Q1 also marks the completion of all GPU replacements. 
So the upward trend noted in the period from 2016-Q4 to 2018-Q1 is
likely due to phased replacements, each time a portion of the machine 
being unavailable, thus having a smaller number of GPUs than the full
machine in operation. 
%\fix{need to verify how long the replacement took}
There is not definitive way to incorporate this unavailability of the
machine into MTBF analysis, unless we know how the down times were scheduled.
The lowest MTBF obtained in 2016-Q4 is 2.7 hours, with subsequent periods having the 
lowest MTBF of 5.9 hours. With system MTBF less than a day, even slight variations in MTBF make it 
difficult to reliably run applications despite using failure recovery approaches such as checkpoint restart, 
as discussed later on in Section~\ref{section:discussion}.

@@

\begin{figure}[bt]
  \begin{center}
    \includegraphics[trim={0 1em 0 1em},clip,width=\columnwidth]{figs/MTBF_quaterly_sys_NewOldALL.pdf}
  \end{center}
  \caption{Variation of system-wide MTBF across hypothetical new and
    old partitions of the machine after a substantial number of new GPUs
were put in service.
DBE and OTB events both determine the MTBF.
Results highlight the difference in reliability for jobs using the new GPUs as compared to old GPUs,
as well as now MTBF is driven by the weaker old partition.}
  \label{fig:MTBF_sys_NewOld}
\end{figure}
We also separate the DBE and OTB failures in this analysis. After the
2017 replacement of many GPUs, there is a drastic increase in
mean-time-between OTB failures, which is also evident in a reduction of OTB failures in \rev{Fig.}~\ref{fig:NumFails_sys}.
However, the system MTBF is determined by the weakest link and here the occurrence of DBE events tends to dictate it.
Even though the replacements helped to increase the MTBF due to DBE events, the overall system 
reliability is dictated by the components with the most age in the
system. There is a re-emergence of an upward trend towards 
the end in DBE failures in \rev{Fig.}~\ref{fig:NumFails_sys}, which
appears to be due to older GPUs in the system.

To better understand the difference in reliability of newer and old portions of the machine, 
\rev{Fig.}~\ref{fig:MTBF_sys_NewOld} shows the drastic difference in system MTBF measured in two hypothetical
partitions of the machine starting from the time when the majority of GPU replacements have been completed. 
The new partition of the machine has a 12X better MTBF than the older
partition.

>>>>

\begin{figure}[bt]
  \begin{center}
    \includegraphics[trim={0 1em 0 1em},clip,width=\columnwidth]{figs/MTBF_GPUwise_yrs_OldNew.pdf}
  \end{center}
  \caption{\rev{Distribution of device-level MTBFs due to failures across all GPUs during the
lifetime of the machine. The DBE and OTB events are separately plotted to distinguish between 
the failure pattern of each event type. Data includes both old and new batch of GPUs with the new GPUs
having MTBFs scattered between 0 and 3 years as highlighted by yellow highlights in the plot. 
Each bin in the distribution represents almost 2 weeks.}}
  \label{fig:Device_MTBFs}
\end{figure}
A histogram of MTBFs measured across GPUs which had at least one failure event is shown 
in \rev{Fig.}~\ref{fig:Device_MTBFs}. This is a practical assessment of device reliabilities 
as opposed to those provided in the device datasheet. The failures are tracked using the
\rev{{\em SN}} of the GPUs even though a GPU might have been placed at different locations in the 
machine during its lifetime. The time to the first failure on a device is measured by taking
the insert time as the reference point, whereas, a simple difference is taken for subsequent
failures. \rev{It can be noticed that MTBFs due to DBE and OTB failures of old GPUs are clustered around 
2.8 years.} This corresponds to the lifetime of most GPUs in the system after accounting 
for relocations and replacements done in the machine. Almost all of the new batch of GPUs lie below 
the average since most have a lifetime close to 3 years. \rev{We point out
that the new batch had a much smaller number of failures (a total of 127 DBEs and OTBs) than
the old batch (a total of 5320 DBEs and OTBs). With this high disproportionality, it is difficult
to compare device-level MTBFs across the new and old batches. On the other hand, it indicates better 
reliability of the new GPUs as highlighted in the next section.}

@@

@@

When GPU replacements start to take place in late 
2016, it triggers a slight increase in MTBF. However, this change only lasts until 2018-Q1, when we see another 
downward trend of system MTBF. Incidentally, 2018-Q1 also marks the completion of all GPU replacements. 
So the upward trend noted in the period from 2016-Q4 to 2018-Q1 is
likely due to phased replacements, each time a portion of the machine 
being unavailable, thus having a smaller number of GPUs than the full
machine in operation. 
There is no definitive way to incorporate this unavailability of the
machine into MTBF analysis, unless we know how the down times were scheduled.
The lowest MTBF obtained in 2016-Q4 is 2.7 hours, with subsequent periods having the 
lowest MTBF of 5.9 hours. With system MTBF less than a day, even slight variations in MTBF make it 
difficult to reliably run applications despite using failure recovery approaches such as checkpoint restart, 
as discussed later on in Section~\ref{section:discussion}.

@@

\begin{figure}[bt]
  \begin{center}
    \includegraphics[trim={0 1em 0 1em},clip,width=\columnwidth]{figs/MTBF_quaterly_sys_NewOldALL_newPart.pdf}
  \end{center}
  \caption{Variation of system-wide MTBF across hypothetical new and
    old partitions of the machine after a substantial number of new GPUs
were put in service. \rev{The dashed line plotted with secondary y-axis shows 
the size of new partition over time. 
DBE and OTB events both determine the MTBF.
Results highlight the difference in reliability for jobs using the new GPUs as compared to old GPUs,
as well as now MTBF is driven by the less reliable old partition despite occupying only a minority
portion of the machine.}}
  \label{fig:MTBF_sys_NewOld}
\end{figure}
We also separate the DBE and OTB failures in this analysis. After the
2017 replacement of many GPUs, there is a drastic increase in
mean-time-between OTB failures, which is also evident in a reduction of OTB failures in \rev{Fig.}~\ref{fig:NumFails_sys}.
However, the system MTBF is determined by the weakest link and here the occurrence of DBE events tends to dictate it.
Even though the replacements helped to increase the MTBF due to DBE events, the overall system 
reliability is dictated by the components with the most age in the
system. There is a re-emergence of an upward trend towards 
the end in DBE failures in \rev{Fig.}~\ref{fig:NumFails_sys}, which
appears to be due to older GPUs in the system.

To better understand the difference in reliability of newer and old portions of the machine, 
\rev{Fig.}~\ref{fig:MTBF_sys_NewOld} shows the drastic difference in system MTBF measured in two hypothetical
partitions of the machine starting from the time when a major number of GPU replacements had been completed.
\rev{The Fig.~\ref{fig:MTBF_sys_NewOld} also shows the proportion of the machine with new GPUs over time. 
The majority of the machine had new GPUs installed starting in 2017-Q3.   
This new partition of the machine has a 12X better MTBF than the older
partition.}
